\documentclass[12pt, a4paper]{article}
\usepackage[table,xcdraw]{xcolor}
\usepackage{soul}
%\usepackage{hyperref}
\usepackage{url}
\usepackage[british]{babel}
\usepackage{csquotes}
\usepackage{ragged2e}
\usepackage{parskip}
%\usepackage[margin=1in]{geometry}
\usepackage[asymmetric, margin=2cm]{geometry}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{graphicx}
\usepackage[hang, flushmargin, bottom]{footmisc}
\usepackage{fontspec}
\usepackage{fancyhdr}
\usepackage{authblk}
\usepackage{indentfirst}

%http://www.hnng.moe/deleteupload.php?key=bcb464b1e6b020ef479420e0d053266e

\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE, RO]{\thepage}
\fancyhead[LO, RE]{Rev. 2017.11}
\fancyhead[CO, CE]{Constitution of The Blair Robot Project}
%\setcounter{page}{0}
\title{Constitution of The Blair Robot Project}
\author{L. Espinoza, U. Das, K. Chang, et. al.}
\affil{Montgomery Blair High School\\ Silver Spring, Maryland}
\date{Revised 2017 November}
\begin{document}
\maketitle
\thispagestyle{empty}
\begin{center}
Typeset in X\kern-.1333em\lower.4ex\hbox{\rotatebox[origin=c]{180}{E}}\kern-.0667em\LaTeX \hspace{.3em}%and B\textsc{ib}\TeX
\end{center}
\clearpage
\begin{center}
\begingroup
\leftskip3.5em
\rightskip\leftskip
\hl{
The key words "MUST", "MUST NOT", "REQUIRED", "SHALL", "SHALL
      NOT", "SHOULD", "SHOULD NOT", "RECOMMENDED",  "MAY", and
      "OPTIONAL" in this document are to be interpreted as described in
      RFC 2119 \footnote{The RFC can be found at \url{https://www.ietf.org/rfc/rfc2119.txt}}.}
\par
\endgroup
\end{center}

\section{Name and Purpose}
\subsection{Name}
The name of this club shall be \textit{the Robotics Team}, \textit{The Blair Robot Project}\hl{,} or \textit{Team 449}.
\subsection{National Affiliation}
\st{The Robotics Club is a member of the FIRST FRC.} \hl{Team 449 is a registered team for the FIRST Robotics Competition (FRC), a national subsidiary organisation of For Inspiration and Recognition of Science and Technology (FIRST).} 
\subsection{Purpose}
The goals and purpose of this club shall be:
\begin{itemize}
\item Create a safe, enthusiastic learning environment in which students can work together and alongside professionals to inspire interest in science, technology, engineering, and mathematics (STEM)\hl{, to develop business and personal skills,} and to provide opportunities for leadership development.
\item Participate in FIRST Robotics Competitions.
\end{itemize}

\section{Membership and Dues}
\subsection{Eligibility}
Membership shall be open to all high school students (regardless of \st{whether they attend Montgomery Blair High School or a Montgomery County Public School}\hl{which high school they attend}) upon payment of the dues as outlined in Section 2.2, \hl{upon agreement to the Code of Conduct as detailed in 2.3, and upon agreement to the Safety Guidelines as detailed in 2.4.}
\subsection{Dues}
Dues shall be \$0 per year.
\subsection{\hl{Code of Conduct}}
\hl{All members of this team must agree to the terms set in the Blair Robot Project Code of Conduct and the contents within. 
Upon the initial establishment of the Code, all changes must be approved in the same manner amendments to this constitution are. 
The code of conduct must always be attached in conjunction with these bylaws.}
\subsection{\hl{Safety Guidelines}}
\hl{
All members must agree to follow the safety guidelines set out in the attached document. Failure to follow these guidelines could result in consequences including, but not limited to, a ban from using power tools, mentor/leadership-student conference, and/or dismissal from the team.
}

\section{Officers}
\subsection{Officers}
The officers shall consist of a President, a Vice President of Finances, Vice President of \st{Operations}\hl{Technology}, and Vice President of Communications.
\subsection{Eligibility}
Anyone that is a member of Team 449 may run for office.  
\subsection{Election}
The officers shall be elected by \st{ballot at the last meeting of the spring semester by a majority of the vote cast for that office.}\hl{the election procedures as in the next section.}

\subsection{\hl{Election Procedures}}
\hl{
All elections in Team 449 must be conducted using standard Instant Runoff Voting procedure. All elections must proceed as follows:}
\begin{enumerate}
\item \hl{A verbal or electronic communication is sent, announcing the date of the election and deadline to apply for a position. This email must contain the application form. The recommended application period is one week.}
\item \hl{Candidates must participate in an open question and answer session with the team membership. It is recommended that this take place at a convenient time for the most number of members.}
\item \hl{At the conclusion of the question and answer session, members will rank the candidates for each position in order from 1 to n, where 1 represents their first preference, and n is the number of candidates. }
\item \hl{When at least two-thirds of the members have voted or at least one week has elapsed, the voting phase may be declared over. After all votes are counted, the candidates in last place are eliminated, and their votes redistributed according to the rankings. This is repeated until one candidate remains. The candidate remaining is declared elected.}
\item \hl{Additional information regarding these procedures can be found at Wikipedia's entry on Instant-runoff Voting.}
\end{enumerate}

\subsection{\hl{Election Transparency}}
\hl{
All decisions conducted through a vote of the team membership must have the anonymised raw vote data released for public inspection, unless the data itself jeopardises the anonymity of the vote. 
The data must not contain any identifying information. 
This data must be stored in an archival location and remain publicly accessible for at least four years. 
The procedures used in the election must also be publicly accessible. 
}

\subsection{Term}
The officers shall serve for one year and their term of office shall begin \st{at the commencement of the fall semester.}\hl{immediately upon the conclusion of swearing-in ceremonies at the end-of-year celebration.}
\subsection{\hl{Removal}}
\hl{An officer may be removed from office if the motion is supported by at least a two-thirds majority of the mentors and Staff Sponsor. 
Such a motion may be proposed by any member of the team to either the lead nontechnical or lead technical mentor, who must query all of the mentors and the Staff Sponsor. 
Only the result (affirm or reject) shall be announced. All vacancies will be filled as outlined in Section 3.6.}
\subsection{Vacancy}
If a vacancy occurs in the office of President, an election among the current Vice Presidents shall take place, and that person shall assume the office for the remainder of the term and vacancies in any other office shall be filled by a special election. 
\hl{These elections shall be conducted according to the procedures in Amendment 10.1}

\section{Duties of Officers}
\subsection{President}
It shall be the duty of the President to:

\begin{itemize}
\item Lead with gracious professionalism.
\item \st{Schedule meetings and set agendas.} \hl{Oversee team schedule throughout the year.}
\begin{itemize}
\item \hl{Schedule meeting times and locations.}
\item \hl{Set agendas.}
\begin{itemize}
\item \hl{Determine participation in competitions, including but not limited to, attendance or drive team membership.}
\end{itemize}
\end{itemize}
\item \hl{Organise larger competition events, such as District Championships and Championships.}
\item Lead weekly meetings with the Vice Presidents\hl{.}
\item \st{Work with team leadership and mentors to determine appropriate}\hl{Review and approve the VP Finances' proposed} budget for the year\hl{.}
\item \st{Coordinate with technical mentors, scheduling mentors, financial mentors, and fundraising mentors.}
\item \hl{Facilitate communication and maintain relationships between all team members – students, mentors, parents, and sponsors.}
\item \hl{Coordinate regular team updates for distribution to team members, mentors, and sponsors.}
\item Run Kickoff and \hl{manage FRC }Build Season.
\item Guide team decision-making process.
\item \st{Mediate and resolve any disagreements during build season.}
\item Work with \hl{the} Vice Presidents and other officers to determine appropriate deadlines for projects.
\item Lead planning of team schedule at competition and events.
\item Communicate robot progress to the team through email/blog updates.
\item \st{Write inspiring e-mails with the Vice Presidents.}
\item \st{Communicate team progress via email and blog to team sponsors.}
\item \hl{Ensure all work is done with safety-trained adult supervision.}
\item Represent \hl{the }team at sponsorship pitches\hl{,} \st{and}competitions\hl{, and to the media}.
\item \st{Arrange coverage for community outreach events.}
\item Run elections for coming year’s officers.  
\item Assist the Vice Presidents with all duties as requested\st{, including}\hl{.}
	\begin{itemize}
		\item \st{Help lead the weekly meetings, scheduling / agendas, maintaining relationships with students and mentors, communication.}
		\item \st{And Any other tasks as requested by the Vice Presidents}
		\item \st{Be familiar with all of the responsibilities of the Vice Presidents and be ready to preside when called on.}
	\end{itemize}
\end{itemize}

\subsection{Vice-President of \st{the} Finances}
It shall be the duty of the Vice-President of Finances to:
\begin{itemize}
\item \hl{Work with mentors and officers to determine an appropriate budget for the fiscal year.}
\item Work to determine an appropriate organization system for the room, teach it to others, and implement it \hl{effectively}\st{in conjunction with the Vice-President of Operations}.
\item Track team finances with financial mentor and report to leadership on budget \hl{each month}.
\item \st{Work with the Public Relations Subteam and financial mentors to develop and maintain sponsorship letters. } 
\item Inventory new incoming parts and to distribute them accordingly \st{in conjunction with the Vice-President of Operations}.
	\begin{itemize}
	\item \st{Serve as the team’s quartermaster: k}\hl{K}eep\st{ing} track of parts orders (ordering and receiving)\st{,}
    \item Maintain\st{ing} a spreadsheet to organize the parts orders\hl{.}
	\item \st{m}\hl{M}anage inventory (accounting for spares, ordering spares, packing spares)\hl{.}
	\item \st{p}\hl{P}romote efficiency in use of financial and human resources\hl{.}
    \item \hl{Coordinate room requests.}
\end{itemize}
\item \st{Write and implement checklists to keep track of what is being packed for competition and outreach events.}
\item \st{Lead robot packing for competition and events in conjunction with the Vice-President of Communications.}
\item \st{Lead the early crew in unpacking and setting up the pit at competition in conjunction with the Vice-President of Communications.}
\item \st{Lead pack-up of the pit after competition in conjunction with the Vice-President of Communications.}
\item \st{Run a blog on Wordpress during build season to keep members updated about the robot design and various events.}
\item \st{Take, type, and distribute minutes of meetings}
\end{itemize}

\subsection{Vice-President of Communications}
It shall be the duty of the Vice-President of Communications to:
\begin{itemize}
\item Communicate and organize any \st{preseason} \hl{off-season competition }events.
\item \st{Work with the President and Vice-Presidents to}\hl{Lead }organi\st{ze}\hl{sation} \st{the} district competitions.
\item \st{Work with the Vice-President of Finances to pack the necessary items for the respective competitions.}
\item Lead robot packing for \st{competition and events in conjunction with the Vice-President of Finances}\hl{outreach events}.
\item \st{Lead the early crew in unpacking and setting up the pit at competition in conjunction with the Vice-President of Finances.}
\item \st{Lead pack-up of the pit after competition in conjunction with the Vice-President of Finances.}
\item Communicate with the Public Relation subteam about outreach events, and to work together to ensure success.
\item Respond to any \hl{external} inquiries about the team\st{, sponsorship, outreach events, etc. in accordance with decisions of the team leadership}.
\item Plan team social events\hl{.}
\item Help mentors with distribution and collection of permission slips and any other paperwork.
\item \hl{Ensure implementation of the Code of Conduct and serve on the Human Resources committee.}
\item \hl{Record and distribute minutes of leadership meetings.}
\end{itemize}

\subsection{Vice-President of \st{Operations}\hl{Technology}}
It shall be the duty of the Vice-President of \st{Operations}\hl{Technology} to:
\begin{itemize}
\item Run FRC Build Season \st{(including kickoff)}, as well as other technical projects:
	\begin{itemize}
		\item Coordinate with subteam leaders to create and maintain project schedules.
		\item Ensure proper integration and communication between subteams.
		\item Assist team members with technical advice and guidance.
		\item Ensure subteams and project teams have appropriate membership levels.
	\end{itemize}
\item Appoint team member to ensure maintenance of proper safety procedures (ie. wearing safety glasses, using tools appropriately) during work hours.
\item \st{Work to determine an appropriate organization system for the room, teach it to others, and implement it in conjunction with the Vice-President of Finances.}
\item \st{Inventory new incoming parts and to distribute them accordingly in conjunction with the Vice-President of Finances.}
\item Oversee and to help the \st{Tech subteam} \hl{designated system administrator} with any computer permissions\hl{.}
\item \st{Make sure all work is supervised by a safety-trained adult.}
\item \hl{Appoint team member to ensure maintenance of proper safety procedures (ie. wearing safety glasses, using tools appropriately) during work hours.}
\item \st{Ensure proper integration and communication between subteams.}
\item \st{Assist people with proper technical advice and guidance.}
\item \st{Ensure people are included in project teams.}
\item \st{Talk to subteams to keep them on schedule.}
\end{itemize}

\section{Meetings}
\subsection{Meetings}
Regular meetings shall be held during the school year. 
Team 449 will meet every Thursday and \st{almost every other weekend (alternating between Saturday and Sunday)} \hl{weekends, subject to the discretion of the Officers}, aside from national holidays, until \st{Jan. 9th}\hl{the day of Kickoff}. 
For the 6.5 weeks after \st{Jan. 9th}\hl{Kickoff},  Team 449 will meet every day of the week.  
These meetings will go from \st{3}\hl{15}:20-\st{6}\hl{18}:30 on weekdays, and 10:00-\st{5}\hl{17}:00 on the weekends\hl{ subject to the discretion of the Officers.}
\subsection{Special Meeting}
\st{Extra meetings on the weekends, or extra meetings at mentors’ houses,}\hl{Additional special meetings} may be scheduled \st{based on need.} \hl{at the discretion of the Officers.}
\subsection{Quorum}
A quorum \hl{for a meeting} shall consist of \hl{at least two members of the Officers, at least two Committee Leaders, at least three additional students,}\st{the student leadership} and at least one mentor.

\section{Executive Committee}
\subsection{Responsibility}
Management of this club shall be vested in the \st{student leadership}\hl{Officers} (consisting of elected positions) responsible to the entire membership to uphold these bylaws.
\subsection{Membership}
This committee shall consist of the Officers as listed in Article 3 and the Faculty Sponsor, as well as \hl{the Lead Technical and Nontechnical}mentors.
\subsection{Meetings}
This committee shall meet as needed with mentors in order to organize and plan future activities. Meetings \st{can}\hl{may} occur during the weekends and during summer breaks if needed.

\section{Staff Sponsor}
\subsection{Selection}
There \st{shall}\hl{must} be a Staff Sponsor who shall be selected each year by the membership.
\subsection{Duties}
The responsibilities of the Staff Sponsor shall be to:
\begin{itemize}
\item Sign building use forms\hl{.}
\item Sign financial \st{acct}\hl{account} forms\hl{.}
\item Submit field trip paperwork \st{-team fills out paperwork, only need signature}
\item Attend competitions - \hl{up to }four school days missed\st{;}\hl{. The} team pays for sub\hl{stitute} time\st{,} \hl{and} travel expenses\hl{.}
\item Open room 361 for team meetings\st{,}\hl{and} work sessions\hl{ when appropriate.}
\item Lend name and credentials to team grants\hl{.}
\item Attend Thursday meetings from \st{3}\hl{15}:20 - \st{4}\hl{16}:30 \st{pm}\hl{.}
\item Inform students about MCPS policies and rules, enforcing them as needed\hl{.}
\end{itemize}

\section{\hl{Additional} Committees}
\subsection{\st{Program Committees}}
\st{A program committee composed of the Vice-President, as Chairperson, and four other members, shall be appointed by the President before the end of spring semester. Their duty shall be to plan the overall program of the club.}
\subsection{Other Committees}
Robotics Club shall be divided into \hl{Committees, henceforth known as }subteams\hl{,} based on the student\hl{s}’\st{s} interests. These subteams are as follows:
\begin{itemize}
\item Mechanics
\item Electronics
\item Programming
\item \st{CAD}
\item Drive
\item \st{Tech}
\item Public Relations
\end{itemize}
All students are free to join whichever subteam, and can be part of one or more. Being a part of a subteam is necessary for being on the team.

\subsubsection{\hl{Subteam Leader Selection}}
\hl{Each subteam must have at least one subteam leader. 
Subject to the discretion of the Officers, a subteam may have more leaders.} \newline
\hl{Subteam leaders are selected by the incoming Officers, with input from outgoing Officers, outgoing subteam leaders, and mentors from candidates who apply for a subteam leadership position. 
At the same time officer elections are conducted, a communication (electronic or otherwise) must be distributed announcing that applications for subteam leader are open. 
The recommended open period is one week. 
At the conclusion of this period, the Executive Committee must fairly and justly review all applications and select up to three subteam leaders for every subteam. 
}


\subsection{\hl{Subteam Leader Removal}}
\hl{A subteam leader may be removed from office if the motion is supported by at least a two-thirds majority of the Executive Committee. Such a motion may be proposed by any member of the team to either the President, who must query the entire Executive Committee. Only the result (affirm or reject) shall be announced. All vacancies will be filled by special appointment of the Executive Committee.
}

\subsection{\hl{Subteam Leader Responsibilities}}
\hl{It shall be the duty of the subteam leaders to:}
\begin{itemize}
\item \hl{Assign tasks to members of their subteam.}
\item \hl{Ensure tasks are completed in a timely and appropriate manner.}
\item \hl{Teach all team members during the general training period and subteam members during the latter half of preseason.}
\item \hl{Plan subteam activities for each meeting, create an agenda/lesson plan, and submit to the Vice President of Technology at least 24 hours before the given meeting.}
\item \hl{Communicate with team members regarding subteam-specific activities, including email reminders and meeting recaps.}
\end{itemize}

\subsection{Special Committees}
The President shall have the authority to appoint any special committees, with the approval of the student leadership, from time to time as \st{need demands}\hl{is needed}.

\section{Amendment\st{s} \hl{Process}}
\subsection{Process}
\st{These bylaws may be amended}\hl{Amendments to these bylaws must be approved} by a two-thirds (2/3) majority vote of the chapter membership.

\subsection{Notice}
All members shall receive advance notice of the proposed amendment at least five days before the meeting. 

\section{\hl{Amendments}}

\subsection{\hl{Permanence of This Document}}
\hl{Upon the approval of this version of the Constitution, the text of the Constitution may not be directly edited, except for formatting and factual corrections. 
Changes to this Constitution may be undertaken by passing amendments to sections or other amendments as set out in Section 9. 
Amendments should begin with the text "Amends Section x". The section of text in the amended section that is changed shall be struck out, but shall not be removed.
As a result, there will be a one week request for comment regarding this document, at the conclusion of which final adjustments to this document will be made.
This amendment, upon its approval, must not be amended by subsequent amendments.}
\end{document}
